\documentclass[]{article}

\newcommand{\HIDE}[1]{}

%opening
\title{Research Summary}
\author{Rick Klomp}

\begin{document}

\maketitle

This PhD has been initiated\footnote{The project is in its initial stages (kickoff was on March 1st).} in pursuit of better understanding the dynamics of applications of Blockchain technology. In short, Blockchain (BC) technology enables to setup a trustable network system wherein each participating node does not need to trust any of the other nodes, nor does it need to know the other node's identities.

BCs are a new phenomena that have some distinctive properties. They are highly concurrent in nature, have an extraordinary amount of parties participating at roughly the same time, and cannot guarantee any safety against malicious behavior (though they can guarantee the probabilities of such behavior achieving success or not). It is due to this combination of properties that existing theory and practice regarding the analysis of software systems does not fit the paradigm.

On the other hand, the technology presents many new possibilities with decent chance of success for companies and startups and as such is widely, and in fact increasingly so, experimented on in practice\footnote{
	The two most widely known applications of Blockchain technology are likely Bitcoin and Ethereum.
}. Especially approaches of BC applications such as Ethereum, where the resulting behavior of the system is for the most part defined by users of the system and not the initial system itself, are prone to errors.

This provides ample motivation for defining a theoretical framework of BC technology through which we can better understand the dynamics of BC applications. It should provide a means to find a suitable paradigm to formally model the behavior of a BC application. With the formal model of a BC, it should be possible to automatically or semi-automatically prove or disprove certain properties.

One such property of interest concerns to what degree the possible interleaving of events can skew what state is ultimately reached by the BC. It is particularly interesting if we can derive from the formal model whether or not some malicious party $p$ can (with certain probability of success) force the BC to reach a, for $p$ desired (and possibly for others undesired), state by using information that due to interleaving effects is processed by the BC \emph{after} an interjected message of $p$.

Another such property of interest concerns the analysis of whether encrypted values communicated through the BC remain secret throughout their lifespan. This is related to a large amount of cryptographic research that has been performed. However, it is not known yet if this directly translates to the semantics of BCs due to the highly concurrent behavior of BCs.

There has been some research performed concerning the behavior of BCs, and especially concerning the behavior of smart contracts (which are pieces of code that define part of Ethereum's behavior, programmed by users of Ethereum). However, this research applies existing modeling theory without having this adjusted to better fit the paradigm, and as such only touched the surface of what may be discoverable. In addition to this body of work, in general our work can be built on top of research concerning modeling paradigms (particularly those that focus on modeling concurrent behavior) and cryptography.

A prototype tool will be built that will be used to verify if the acquired theory correctly reflects BC behavior in practice. At least one realistic case study will be performed that involves applying the prototype to a real implementation of Blockchain technology (Wallet Services' application of BC technology). Besides this there may be other case studies performed if required.

Some properties may be provably correct from the theoretical framework itself. For example, the approach that will be taken to prove whether the resulting protocol of the BC maintains secrecy of certain values during their entire lifetime may be provably sound and/or complete. Such properties do not need to be verified through experimental means. However, it will still be interesting to discover through experimental means in what aspects BC applications may tend to lack these properties.

Other properties of these systems are by nature stochastic. For example, if there exists a possibility for a malicious party to interject a message before another one due to \emph{possible} certain interleaving of these messages, then such an attack will have a probability of success. Should the theoretical framework provide a means to derive the probability automatically (within some margin of error), then it will be necessary to verify correctness through experimental means. The verification will then be based on statistical analysis.

Though the case study that is enabled by Wallet Services should provide a decent means to verify the theoretical framework and their data points are of large proportion, it will only put the framework to test on one particular application of BC technology. It will thus be important to additionally apply the prototype to other kinds of BC applications. An alternative option is to define case studies where certain properties are derived from artificial formal model instances. Where the formal model is defined through some automated process, enabling a high amount of different kinds of models to be tested. However, this approach would then need to be provably correct as it needs to be representative to real case scenarios. It is not yet known how this can be ensured. Presumably this may differ significantly depending on what paradigm the formal model will be based.





\HIDE{
\clearpage

\section{Pre-exercise questions}
\subsection{What are the aims and objectives?}
The aim is:
\begin{itemize}
	\item to better understand the dynamics of blockchain derived systems
	\item to enable/improve the formal modeling itself of these systems
 	\item to enable/imporve the formal modeling of the machinery that is employed ontop of these systems
	\item to automatically or semi automatically infer properties from the formal models. Properties of interest are, for example, but not limited to:
	\begin{itemize}
		\item Secrecy (is the secrecy of a certain value kept over the encryption-decryption path?)
		\item Interleaving effects (can some party for example reach some for him desired, but for others undesired, state due to a certain interleaving of events)
	\end{itemize}
\end{itemize}

\subsection{What is the motivation of the project?}
Blockchains are a new phenomena that have some distinctive properties. They are highly concurrent in nature, have an extraordinary amount of parties participating at roughly the same time, and cannot guarantee any safety against malicious behavior (though they can guarantee the probabilities of such behavior achieving success or not).
It is due to these properties that existing theory and practice regarding the analysis of software systems does not fit the paradigm.

On the other hand, the technology presents many new possible venues for companies and startups and as such is widely, and in fact increasingly so, experimented on in practice. This provides ample motivation for building/improving a theoretical framework of Blockchain technology.

\subsection{What are the main pieces of related work?}
There has been some research performed concerning smart contracts. However, this research has only touched the surface of what may be discoverable since it applies existing modeling theory without having this adjusted to better fit the paradigm.

In general our work can/should be built on top of existing knowledge from the following areas.
\begin{itemize}
	\item Blockchain related systems.
	\item Modeling paradigms. In particular those that focus on modeling concurrent behavior.
	\item Cryptography.
\end{itemize}

\subsection{What is the novel idea?}
The notion that we must first acquire/develop a modeling paradigm that fits Blockchain technology's properties.

\subsection{What are the claims or hypotheses?}
The prototype that will be built to perform case studies should be capable to more accurately model a Blockchain's (or/and the machinery that is employed ontop of it) behavior.

\subsection{What kind of evidence will be needed to support these claims or hypotheses?}
Most evidence will likely be of theoretical nature. However, some properties of these systems are by nature stochastic. Evidence of these properties must thus be found through experimental means.

A big case study will involve applying the prototype to a real implementation of Blockchain technology (at Wallet Services).

\subsection{At what stage is the project?}
Initial stage (2 months in).
}
\end{document}
